Leaf traits drive differences in biomass partitioning among major plant functional types

### 2014-12-16 manuscript.Rnw
Add tree to Figure 1. Closes #8

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{Figure1.pdf}
    \caption{(a) Global coverage of the climate space by the dataset. Hexagons are terrestrial observations, excluding areas without woody vegetation, colored by number of 0.5\degree~cells. (b) Schematic of a woody plant, and the variables considered in this study. H = plant height, $A_S$ basal stem area, $A_{sbh}$ stem area at 'breast height', $M_W$ woody biomass, $M_F$ leaf biomass (total aboveground biomass $M_T = M_F + M_W$), $A_F$ total leaf area.}
    \label{fig:figure1}
\end{figure}

>>>>

Figure 1 coutresy of Lana Heydon, IAN Image Library http://ian.umces.edu/imagelibrary.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{Figure1.pdf}
    \caption{\textbf{Overview of the global biomass and allometry database.} (a) Variables were measured on \Sexpr{nrow(dataset)} individual plants from \Sexpr{length(unique(dataset$species))} species. (b) Coverage of the dataset across global climate space. Grey hexagons indicate the number of 0.5\degree~cells with woody vegetation across the space. Colour symbols show the locations of sampled individuals for three dominat woody functional types.}
    \label{fig:figure1}
\end{figure}
